Nic Steyn

### 2025-04-18 site/index.qmd
added survey smoothing paper

My thesis focuses on robust statistical methods for analysing infectious disease dynamics with an emphasis on flexible methodology and [valid uncertainty quantification](https://github.com/nicsteyn2/RobustRtEstimators). My research combines Bayesian inference, [sequential Monte Carlo methods](http://nicsteyn2.github.io/SMCforRt/), and epidemiological modelling, with applications to standard epidemiological data, as well as survey data and [wastewater-based surveillance](https://github.com/nicsteyn2/NZWastewaterModelling).

>>>>

My thesis focuses on robust statistical methods for analysing infectious disease dynamics with an emphasis on flexible methodology and [valid uncertainty quantification](https://github.com/nicsteyn2/RobustRtEstimators). My research combines Bayesian inference, [sequential Monte Carlo methods](http://nicsteyn2.github.io/SMCforRt/), and epidemiological modelling, with applications to standard epidemiological data, as well as [survey data](https://doi.org/10.1101/2025.04.16.25325936) ([see also]((https://doi.org/10.1101/2025.03.03.25323250))) and [wastewater-based surveillance](https://github.com/nicsteyn2/NZWastewaterModelling).
